Comparing tool variability and numerical variability in fMRI analyses

### 2021-11-09 paper/paper.tex
edits in method

\tristan{To be discussed with Ali, this paragraph explains what was done but not 
the purpose or the result of it.}
The presented method does not require any particular software
instrumentation in the data analysis code: it only assumes that executables
are dynamically linked against GNU libc. For this purpose, (1) we captured
the list of dynamic library dependencies using the \texttt{ldd} Linux
utility for the software executables, (2) we traced the system library
calls using \texttt{ltrace} Linux program while running the pipeline
processes.

@@

Further, from the thresholded maps, we determined regional Dice
coefficients between activation clusters in the 360 regions in the Human
Connectome Project Multi-Modal Parcellation atlas version 1.0
(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, Dice coefficients were
computed between activation maps produced by any pair of tools. For WT,
Dice coefficients were computed pair-wise among the three Fuzzy samples of
a given tool and averaged. All Dice coefficients were normalized by the
region size \tristan{how?}.

@@

  %%%%%%%%%% Corr. plot of tstats%%%%%%%%
  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \hfill
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std/correlated-unthresh.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \caption{
        Voxel-wise comparison of BT and WT variabilty. The bottom row represents 
        voxels where the BT/WT ration is in (0.5, 2).}
    \label{fig:unthresh-correlation}
    \end{minipage}}
  \end{figure*}

>>>>

\tristan{
Explain how the instrumentation was validated:
\begin{enumerate}
\item Verify that two consecutive IEEE executions are identical (no random effects)
\item Verify that all pipelines use libm
\item List all the dependencies of all the pipelines using ldd 
\item Verify that no math function is implemented in these dependencies
\item Verify that fuzzy libmat has an effect on the results
\end{enumerate}
}

@@

Further, from the thresholded maps, we determined regional Dice
coefficients between activation clusters in the 360 regions in the Human
Connectome Project Multi-Modal Parcellation atlas version 1.0
(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, Dice coefficients were
computed between activation maps produced by any pair of tools. For WT,
Dice coefficients were computed pair-wise among the three Fuzzy samples of
a given tool and averaged. All Dice coefficients were normalized by the
region size \tristan{explain how you did this: x = (dice x region size) ; x = (x-xmin)/(xmax-xmin)}.

@@

  %%%%%%%%%% Corr. plot of tstats%%%%%%%%
  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \hfill
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std/correlated-unthresh.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \caption{
        Voxel-wise comparison of BT and WT variabilty. The bottom row represents 
        voxels where the BT/WT ratio is in (0.5, 2).}
    \label{fig:unthresh-correlation}
    \end{minipage}}
  \end{figure*}
